\Large \bf Evaluating eBPF as a Platform for Congestion Control Algorithm

### 2024-12-12 paper/sections/evaluation.tex
chore: minor fixes

\subsection{Setup and Method}
An alternative implementation of an existing CCA can be evaluated using two metrics.
We evaluate eBPFCCP using two metrics:
\begin{enumerate}
    \item {\bf Behavior}: how accurate is eBPFCCP in replicating original CCA behavior?
    \item {\bf Performance}: what is the performance overhead of eBPFCCP?
\end{enumerate}

@@

The results of the behavioral benchmarks are shown in Figures~\ref{fig:cca-behavior-cwnd},~\ref{fig:cca-behavior-bitrate}, and~\ref{fig:cca-behavior-rtt}. From the graphs, we can see that the behavior of the same Congestion Control Algorithm remains similar across congestion window size, bitrate, and RTT. The results of the CPU benchmarks are shown in Figure \ref{fig:cca-performance}. The eBPF implementation of TCP Cubic achieved similar CPU performance compared to the built-in Linux kernel networking stack implementation. CCP-Cubic from the CCP Project \cite{generic-cong-avoid} combined with the CCP datapath kernel module and netlink slightly lower performance, where its median is at 91 percent of the full kernel implementation value. Our implementation of eBPFCCP ranked lower on the performance chart, but was still able to achieve 80 percent of the full kernel implementation value. Due to the relative comparability of CPU performance between the kernel and eBPF implementations of TCP Cubicm, we theorize the gap between eBPFCCP and kernel module CCP was due to our choice of using unix pipes rather than netlink as a channel for communicating between the eBPFCCP and the user space program. \\
From these results, we can conclude that eBPF is a viable platform for the development CCAs. The minor performance overhead when compared to the kernel native implementation suggests that eBPF-based CCAs can be used as a long-term deployment option outside of research and development stages. With regards to CCP, while the performance overhead of eBPFCCP is non-negligible, it should be noted that the benchmark is performed on a single core VM. In a real-world scenario, the performance overhead of eBPFCCP is likely to be negligible for all but the most performance-sensitive industry networking applications. The safety guarantees provided by eBPFCCP would provide a good intermediate step for users to adopt and experiment with a new CCA before it is natively implemented either directly into the kernel or as an eBPF program. 
\end{document}

>>>>

\subsection{Setup and Method}
An alternative implementation of an existing CCA can be evaluated using two metrics.
We evaluate eBPFCCP using two metrics:
\begin{enumerate}
    \item {\bf Behavior}: how accurate is an alternative implementation in replicating original CCA behavior?
    \item {\bf Performance}: what is the performance overhead of the alternative implementation?
\end{enumerate}

@@

The results of the behavioral benchmarks are shown in Figures~\ref{fig:cca-behavior-cwnd},~\ref{fig:cca-behavior-bitrate}, and~\ref{fig:cca-behavior-rtt}. From the graphs, we can see that the behavior of the same Congestion Control Algorithm remains similar across congestion window size, bitrate, and RTT. The results of the CPU benchmarks are shown in Figure \ref{fig:cca-performance}. The eBPF implementation of TCP Cubic achieved similar CPU performance compared to the built-in Linux kernel networking stack implementation. CCP-Cubic from the CCP Project \cite{generic-cong-avoid} combined with the CCP datapath kernel module and netlink slightly lower performance, where its median is at 91 percent of the full kernel implementation value. Our implementation of eBPFCCP ranked lower on the performance chart, but was still able to achieve 80 percent of the full kernel implementation value. Due to the relative comparability of CPU performance between the kernel and eBPF implementations of TCP Cubic, we theorize the gap between eBPFCCP and kernel module CCP was due to our choice of using unix pipes rather than netlink as a channel for communicating between the eBPFCCP and the user space program. \\
From these results, we can conclude that eBPF is a viable platform for the development CCAs. The minor performance overhead when compared to the kernel native implementation suggests that eBPF-based CCAs can be used as a long-term deployment option outside of research and development stages. With regards to CCP, while the performance overhead of eBPFCCP is non-negligible, it should be noted that the benchmark is performed on a single core VM. In a real-world scenario, the performance overhead of eBPFCCP is likely to be negligible for all but the most performance-sensitive industry networking applications. The safety guarantees provided by eBPFCCP would provide a good intermediate step for users to adopt and experiment with a new CCA before it is natively implemented either directly into the kernel or as an eBPF program. 
\end{document}
